Pengetahuan dan Kemampuan yang Dimiliki Pengguna Non-Ahli dalam Mendeteksi Phishing

### 2024-12-28 paper.tex
fixing kerangka

\section{The Design, Intent, and \\ Limitations of the Templates}
The templates are intended to {\bf{approximate the final look and page length
      of the articles/papers}}. {\bf{They are NOT intended to be the final produced
  work that is displayed in print or on
  IEEEXplore\textsuperscript{\textregistered}}}. They will help to give the
authors an approximation of the number of pages that will be in the final
version. The structure of the \LaTeX\ files, as designed, enable easy
conversion to XML for the composition systems used by the IEEE. The XML files
are used to produce the final print/IEEEXplore pdf and then converted to HTML
for IEEEXplore.

\section{Where to Get \LaTeX \ Help --- User Groups}
The following online groups are helpful to beginning and experienced \LaTeX\
users. A search through their archives can provide many answers to common
questions.
\begin{list}{}{}
  \item{\url{http://www.latex-community.org/}}
  \item{\url{https://tex.stackexchange.com/} }
\end{list}

\section{Other Resources}
See \cite{ref1,ref2,ref3,ref4,ref5} for resources on formatting math into text
and additional help in working with \LaTeX .

\section{Text}
For some of the remainer of this sample we will use dummy text to fill out
paragraphs rather than use live text that may violate a copyright.

Itam, que ipiti sum dem velit la sum et dionet quatibus apitet voloritet audam,
qui aliciant voloreicid quaspe volorem ut maximusandit faccum conemporerum aut
ellatur, nobis arcimus. Fugit odi ut pliquia incitium latum que cusapere perit
molupta eaquaeria quod ut optatem poreiur? Quiaerr ovitior suntiant litio
bearciur?

Onseque sequaes rectur autate minullore nusae nestiberum, sum voluptatio. Et
ratem sequiam quaspername nos rem repudandae volum consequis nos eium aut as
molupta tectum ulparumquam ut maximillesti consequas quas inctia cum
volectinusa porrum unt eius cusaest exeritatur? Nias es enist fugit pa vollum
reium essusam nist et pa aceaqui quo elibusdandis deligendus que nullaci
lloreri bla que sa coreriam explacc atiumquos simolorpore, non prehendunt lam
que occum\cite{ref6} si aut aut maximus eliaeruntia dia sequiamenime natem
sendae ipidemp orehend uciisi omnienetus most verum, ommolendi omnimus, est,
veni aut ipsa volendelist mo conserum volores estisciis recessi nveles ut
poressitatur sitiis ex endi diti volum dolupta aut aut odi as eatquo cullabo
remquis toreptum et des accus dolende pores sequas dolores tinust quas expel
moditae ne sum quiatis nis endipie nihilis etum fugiae audi dia quiasit quibus.
\IEEEpubidadjcol Ibus el et quatemo luptatque doluptaest et pe volent rem
ipidusa eribus utem venimolorae dera qui acea quam etur aceruptat. Gias anis
doluptaspic tem et aliquis alique inctiuntiur?

Sedigent, si aligend elibuscid ut et ium volo tem eictore pellore ritatus ut ut
ullatus in con con pere nos ab ium di tem aliqui od magnit repta volectur
suntio. Nam isquiante doluptis essit, ut eos suntionsecto debitiur sum ea
ipitiis adipit, oditiore, a dolorerempos aut harum ius, atquat.

Rum rem ditinti sciendunti volupiciendi sequiae nonsect oreniatur, volores
sition ressimil inus solut ea volum harumqui to see\eqref{deqn_ex1a} mint aut
quat eos explis ad quodi debis deliqui aspel earcius.

\begin{equation}
  \label{deqn_ex1a}
  x = \sum_{i=0}^{n} 2{i} Q.
\end{equation}

Alis nime volorempera perferi sitio denim repudae pre ducilit atatet volecte
ssimillorae dolore, ut pel ipsa nonsequiam in re nus maiost et que dolor sunt
eturita tibusanis eatent a aut et dio blaudit reptibu scipitem liquia
consequodi od unto ipsae. Et enitia vel et experferum quiat harum sa net faccae
dolut voloria nem. Bus ut labo. Ita eum repraer rovitia samendit aut et volupta
tecupti busant omni quiae porro que nossimodic temquis anto blacita conse nis
am, que ereperum eumquam quaescil imenisci quae magnimos recus ilibeaque cum
etum iliate prae parumquatemo blaceaquiam quundia dit apienditem rerit re eici
quaes eos sinvers pelecabo. Namendignis as exerupit aut magnim ium illabor
roratecte plic tem res apiscipsam et vernat untur a deliquaest que non cus eat
ea dolupiducim fugiam volum hil ius dolo eaquis sitis aut landesto quo corerest
et auditaquas ditae voloribus, qui optaspis exero cusa am, ut plibus.

\section{Some Common Elements}
\subsection{Sections and Subsections}
Enumeration of section headings is desirable, but not required. When numbered,
please be consistent throughout the article, that is, all headings and all
levels of section headings in the article should be enumerated. Primary
headings are designated with Roman numerals, secondary with capital letters,
tertiary with Arabic numbers; and quaternary with lowercase letters. Reference
and Acknowledgment headings are unlike all other section headings in text. They
are never enumerated. They are simply primary headings without labels,
regardless of whether the other headings in the article are enumerated.

\subsection{Citations to the Bibliography}
The coding for the citations is made with the \LaTeX\ $\backslash${\tt{cite}}
command. This will display as: see \cite{ref1}.

For multiple citations code as follows:
{\tt{$\backslash$cite\{ref1,ref2,ref3\}}} which will produce
\cite{ref1,ref2,ref3}. For reference ranges that are not consecutive code as
  {\tt{$\backslash$cite\{ref1,ref2,ref3,ref9\}}} which will produce
\cite{ref1,ref2,ref3,ref9}

\subsection{Lists}
In this section, we will consider three types of lists: simple unnumbered,
numbered, and bulleted. There have been many options added to IEEEtran to
enhance the creation of lists. If your lists are more complex than those shown
below, please refer to the original ``IEEEtran\_HOWTO.pdf'' for additional
options.\\

\subsubsection*{\bf A plain  unnumbered list}
\begin{list}{}{}
  \item{bare\_jrnl.tex}
  \item{bare\_conf.tex}
  \item{bare\_jrnl\_compsoc.tex}
  \item{bare\_conf\_compsoc.tex}
  \item{bare\_jrnl\_comsoc.tex}
\end{list}

\subsubsection*{\bf A simple numbered list}
\begin{enumerate}
  \item{bare\_jrnl.tex}
  \item{bare\_conf.tex}
  \item{bare\_jrnl\_compsoc.tex}
  \item{bare\_conf\_compsoc.tex}
  \item{bare\_jrnl\_comsoc.tex}
\end{enumerate}

\subsubsection*{\bf A simple bulleted list}
\begin{itemize}
  \item{bare\_jrnl.tex}
  \item{bare\_conf.tex}
  \item{bare\_jrnl\_compsoc.tex}
  \item{bare\_conf\_compsoc.tex}
  \item{bare\_jrnl\_comsoc.tex}
\end{itemize}

\subsection{Figures}
Fig. 1 is an example of a floating figure using the graphicx package. Note that
$\backslash${\tt{label}} must occur AFTER (or within)
$\backslash${\tt{caption}}. For figures, $\backslash${\tt{caption}} should
occur after the $\backslash${\tt{includegraphics}}.

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{fig1}
  \caption{Simulation results for the network.}
  \label{fig_1}
\end{figure}

Fig. 2(a) and 2(b) is an example of a double column floating figure using two
subfigures. (The subfig.sty package must be loaded for this to work.) The
subfigure $\backslash${\tt{label}} commands are set within each subfloat
command, and the $\backslash${\tt{label}} for the overall figure must come
after $\backslash${\tt{caption}}. $\backslash${\tt{hfil}} is used as a
separator to get equal spacing. The combined width of all the parts of the
figure should do not exceed the text width or a line break will occur.
%
\begin{figure*}[!t]
  \centering
  \subfloat[]{\includegraphics[width=2.5in]{fig1}%
    \label{fig_first_case}}
  \hfil
  \subfloat[]{\includegraphics[width=2.5in]{fig1}%
    \label{fig_second_case}}
  \caption{Dae. Ad quatur autat ut porepel itemoles dolor autem fuga. Bus quia con nessunti as remo di quatus non perum que nimus. (a) Case I. (b) Case II.}
  \label{fig_sim}
\end{figure*}

Note that often IEEE papers with multi-part figures do not place the labels
within the image itself (using the optional argument to
$\backslash${\tt{subfloat}}[]), but instead will reference/describe all of them
(a), (b), etc., within the main caption. Be aware that for subfig.sty to
generate the (a), (b), etc., subfigure labels, the optional argument to
$\backslash${\tt{subfloat}} must be present. If a subcaption is not desired,
leave its contents blank, e.g.,$\backslash${\tt{subfloat}}[].

\section{Tables}
Note that, for IEEE-style tables, the $\backslash${\tt{caption}} command should
come BEFORE the table. Table captions use title case. Articles (a, an, the),
coordinating conjunctions (and, but, for, or, nor), and most short prepositions
are lowercase unless they are the first or last word. Table text will default
to $\backslash${\tt{footnotesize}} as the IEEE normally uses this smaller font
for tables. The $\backslash${\tt{label}} must come after
$\backslash${\tt{caption}} as always.

\begin{table}[!t]
  \caption{An Example of a Table\label{tab:table1}}
  \centering
  \begin{tabular}{|c||c|}
    \hline
    One   & Two  \\
    \hline
    Three & Four \\
    \hline
  \end{tabular}
\end{table}

\section{Algorithms}
Algorithms should be numbered and include a short title. They are set off from
the text with rules above and below the title and after the last line.

\begin{algorithm}[H]
  \caption{Weighted Tanimoto ELM.}\label{alg:alg1}
  \begin{algorithmic}
    \STATE
    \STATE {\textsc{TRAIN}}$(\mathbf{X} \mathbf{T})$
    \STATE \hspace{0.5cm}$ \textbf{select randomly } W \subset \mathbf{X}  $
    \STATE \hspace{0.5cm}$ N_\mathbf{t} \gets | \{ i : \mathbf{t}_i = \mathbf{t} \} | $ \textbf{ for } $ \mathbf{t}= -1,+1 $
    \STATE \hspace{0.5cm}$ B_i \gets \sqrt{ \textsc{max}(N_{-1},N_{+1}) / N_{\mathbf{t}_i} } $ \textbf{ for } $ i = 1,...,N $
    \STATE \hspace{0.5cm}$ \hat{\mathbf{H}} \gets  B \cdot (\mathbf{X}^T\textbf{W})/( \mathbb{1}\mathbf{X} + \mathbb{1}\textbf{W} - \mathbf{X}^T\textbf{W} ) $
    \STATE \hspace{0.5cm}$ \beta \gets \left ( I/C + \hat{\mathbf{H}}^T\hat{\mathbf{H}} \right )^{-1}(\hat{\mathbf{H}}^T B\cdot \mathbf{T})  $
    \STATE \hspace{0.5cm}\textbf{return}  $\textbf{W},  \beta $
    \STATE /[11]
    \STATE {\textsc{PREDICT}}$(\mathbf{X} )$
    \STATE \hspace{0.5cm}$ \mathbf{H} \gets  (\mathbf{X}^T\textbf{W} )/( \mathbb{1}\mathbf{X}  + \mathbb{1}\textbf{W}- \mathbf{X}^T\textbf{W}  ) $
    \STATE \hspace{0.5cm}\textbf{return}  $\textsc{sign}( \mathbf{H} \beta )$
  \end{algorithmic}
  \label{alg1}
\end{algorithm}

Que sunt eum lam eos si dic to estist, culluptium quid qui nestrum nobis
reiumquiatur minimus minctem. Ro moluptat fuga. Itatquiam ut laborpo rersped
exceres vollandi repudaerem. Ulparci sunt, qui doluptaquis sumquia ndestiu
sapient iorepella sunti veribus. Ro moluptat fuga. Itatquiam ut laborpo rersped
exceres vollandi repudaerem.
\section{Mathematical Typography \\ and Why It Matters}

Typographical conventions for mathematical formulas have been developed to {\bf
    provide uniformity and clarity of presentation across mathematical texts}. This
enables the readers of those texts to both understand the author's ideas and to
grasp new concepts quickly. While software such as \LaTeX \ and
MathType\textsuperscript{\textregistered} can produce aesthetically pleasing
math when used properly, it is also very easy to misuse the software,
potentially resulting in incorrect math display.

IEEE aims to provide authors with the proper guidance on mathematical
typesetting style and assist them in writing the best possible article. As
such, IEEE has assembled a set of examples of good and bad mathematical
typesetting \cite{ref1,ref2,ref3,ref4,ref5}.

Further examples can be found at
\url{http://journals.ieeeauthorcenter.ieee.org/wp-content/uploads/sites/7/IEEE-Math-Typesetting-Guide-for-LaTeX-Users.pdf}

\subsection{Display Equations}
The simple display equation example shown below uses the ``equation''
environment. To number the equations, use the $\backslash${\tt{label}} macro to
create an identifier for the equation. LaTeX will automatically number the
equation for you.
\begin{equation}
  \label{deqn_ex1}
  x = \sum_{i=0}^{n} 2{i} Q.
\end{equation}

\noindent is coded as follows:
\begin{verbatim}
\begin{equation}
\label{deqn_ex1}
x = \sum_{i=0}^{n} 2{i} Q.
\end{equation}
\end{verbatim}

To reference this equation in the text use the $\backslash${\tt{ref}} macro.
Please see (\ref{deqn_ex1})\\ \noindent is coded as follows:
\begin{verbatim}
Please see (\ref{deqn_ex1})\end{verbatim}

\subsection{Equation Numbering}
{\bf{Consecutive Numbering:}} Equations within an article are numbered consecutively from the beginning of the
article to the end, i.e., (1), (2), (3), (4), (5), etc. Do not use roman numerals or section numbers for equation numbering.

\noindent {\bf{Appendix Equations:}} The continuation of consecutively numbered equations is best in the Appendix, but numbering
as (A1), (A2), etc., is permissible.\\

\noindent {\bf{Hyphens and Periods}}: Hyphens and periods should not be used in equation numbers, i.e., use (1a) rather than
(1-a) and (2a) rather than (2.a) for subequations. This should be consistent throughout the article.

\subsection{Multi-Line Equations and Alignment}
Here we show several examples of multi-line equations and proper alignments.

\noindent {\bf{A single equation that must break over multiple lines due to length with no specific alignment.}}
\begin{multline}
  \text{The first line of this example}\\
  \text{The second line of this example}\\
  \text{The third line of this example}
\end{multline}

\noindent is coded as:
\begin{verbatim}
\begin{multline}
\text{The first line of this example}\\
\text{The second line of this example}\\
\text{The third line of this example}
\end{multline}
\end{verbatim}

\noindent {\bf{A single equation with multiple lines aligned at the = signs}}
\begin{align}
  a & = c+d \\
  b & = e+f
\end{align}
\noindent is coded as:
\begin{verbatim}
\begin{align}
a &= c+d \\
b &= e+f
\end{align}
\end{verbatim}

The {\tt{align}} environment can align on multiple points as shown in the
following example:
\begin{align}
  x  & = y  & X  & =Y  & a  & =bc \\
  x' & = y' & X' & =Y' & a' & =bz
\end{align}
\noindent is coded as:
\begin{verbatim}
\begin{align}
x &= y & X & =Y & a &=bc\\
x' &= y' & X' &=Y' &a' &=bz
\end{align}
\end{verbatim}

\subsection{Subnumbering}
The amsmath package provides a {\tt{subequations}} environment to facilitate
subnumbering. An example:

\begin{subequations}\label{eq:2}
  \begin{align}
    f            & =g \label{eq:2A}             \\
    f'           & =g' \label{eq:2B}            \\
    \mathcal{L}f & = \mathcal{L}g \label{eq:2c}
  \end{align}
\end{subequations}

\noindent is coded as:
\begin{verbatim}
\begin{subequations}\label{eq:2}
\begin{align}
f&=g \label{eq:2A}\\
f' &=g' \label{eq:2B}\\
\mathcal{L}f &= \mathcal{L}g \label{eq:2c}
\end{align}
\end{subequations}

\end{verbatim}

\subsection{Matrices}
There are several useful matrix environments that can save you some keystrokes.
See the example coding below and the output.

\noindent {\bf{A simple matrix:}}
\begin{equation}
  \begin{matrix}  0 & 1 \\
                1 & 0\end{matrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{matrix}  0 &  1 \\ 
1 &  0 \end{matrix}
\end{equation}
\end{verbatim}

\noindent {\bf{A matrix with parenthesis}}
\begin{equation}
  \begin{pmatrix} 0 & -i \\
                i & 0\end{pmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{pmatrix} 0 & -i \\
 i &  0 \end{pmatrix}
\end{equation}
\end{verbatim}

\noindent {\bf{A matrix with square brackets}}
\begin{equation}
  \begin{bmatrix} 0 & -1 \\
                1 & 0\end{bmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{bmatrix} 0 & -1 \\ 
1 &  0 \end{bmatrix}
\end{equation}
\end{verbatim}

\noindent {\bf{A matrix with curly braces}}
\begin{equation}
  \begin{Bmatrix} 1 & 0  \\
                0 & -1\end{Bmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{Bmatrix} 1 &  0 \\ 
0 & -1 \end{Bmatrix}
\end{equation}\end{verbatim}

\noindent {\bf{A matrix with single verticals}}
\begin{equation}
  \begin{vmatrix} a & b \\
                c & d\end{vmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{vmatrix} a &  b \\ 
c &  d \end{vmatrix}
\end{equation}\end{verbatim}

\noindent {\bf{A matrix with double verticals}}
\begin{equation}
  \begin{Vmatrix} i & 0  \\
                0 & -i\end{Vmatrix}
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\begin{Vmatrix} i &  0 \\ 
0 & -i \end{Vmatrix}
\end{equation}\end{verbatim}

\subsection{Arrays}
The {\tt{array}} environment allows you some options for matrix-like equations.
You will have to manually key the fences, but there are other options for
alignment of the columns and for setting horizontal and vertical rules. The
argument to {\tt{array}} controls alignment and placement of vertical rules.

A simple array
\begin{equation}
  \left(
  \begin{array}{cccc}
    a+b+c & uv  & x-y & 27  \\
    a+b   & u+v & z   & 134
  \end{array}\right)
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\left(
\begin{array}{cccc}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array} \right)
\end{equation}
\end{verbatim}

A slight variation on this to better align the numbers in the last column
\begin{equation}
  \left(
  \begin{array}{cccr}
    a+b+c & uv  & x-y & 27  \\
    a+b   & u+v & z   & 134
  \end{array}\right)
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\left(
\begin{array}{cccr}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array} \right)
\end{equation}
\end{verbatim}

An array with vertical and horizontal rules
\begin{equation}
  \left( \begin{array}{c|c|c|r}
    a+b+c & uv  & x-y & 27  \\ \hline
    a+b   & u+v & z   & 134
  \end{array}\right)
\end{equation}
is coded as:
\begin{verbatim}
\begin{equation}
\left(
\begin{array}{c|c|c|r}
a+b+c & uv & x-y & 27\\
a+b & u+v & z & 134
\end{array} \right)
\end{equation}
\end{verbatim}
Note the argument now has the pipe "$\vert$" included to indicate the placement
of the vertical rules.

\subsection{Cases Structures}
Many times cases can be miscoded using the wrong environment, i.e.,
{\tt{array}}. Using the {\tt{cases}} environment will save keystrokes (from not
having to type the $\backslash${\tt{left}}$\backslash${\tt{lbrace}}) and
automatically provide the correct column alignment.
\begin{equation*}
  {z_m(t)} = \begin{cases}
    1,   & {\text{if}}\ {\beta }_m(t) \\
    {0,} & {\text{otherwise.}}
  \end{cases}
\end{equation*}
\noindent is coded as follows:
\begin{verbatim}
\begin{equation*}
{z_m(t)} = 
\begin{cases}
1,&{\text{if}}\ {\beta }_m(t),\\ 
{0,}&{\text{otherwise.}} 
\end{cases}
\end{equation*}
\end{verbatim}
\noindent Note that the ``\&'' is used to mark the tabular alignment. This is important to get  proper column alignment. Do not use $\backslash${\tt{quad}} or other fixed spaces to try and align the columns. Also, note the use of the $\backslash${\tt{text}} macro for text elements such as ``if'' and ``otherwise.''

\subsection{Function Formatting in Equations}
Often, there is an easy way to properly format most common functions. Use of
the $\backslash$ in front of the function name will in most cases, provide the
correct formatting. When this does not work, the following example provides a
solution using the $\backslash${\tt{text}} macro:

\begin{equation*}
  d_{R}^{KM} = \underset {d_{l}^{KM}} {\text{arg min}} \{ d_{1}^{KM},\ldots,d_{6}^{KM}\}.
\end{equation*}

\noindent is coded as follows:
\begin{verbatim}
\begin{equation*} 
 d_{R}^{KM} = \underset {d_{l}^{KM}} 
 {\text{arg min}} \{ d_{1}^{KM},
 \ldots,d_{6}^{KM}\}.
\end{equation*}
\end{verbatim}

\subsection{ Text Acronyms Inside Equations}
This example shows where the acronym ``MSE" is coded using
$\backslash${\tt{text\{\}}} to match how it appears in the text.

\begin{equation*}
  \text{MSE} = \frac {1}{n}\sum _{i=1}^{n}(Y_{i} - \hat {Y_{i}})^{2}
\end{equation*}

\begin{verbatim}
\begin{equation*}
 \text{MSE} = \frac {1}{n}\sum _{i=1}^{n}
(Y_{i} - \hat {Y_{i}})^{2}
\end{equation*}
\end{verbatim}

\section{Conclusion}
The conclusion goes here.

@@

  {\appendix[Proof of the Zonklar Equations]
    Use $\backslash${\tt{appendix}} if you have a single appendix:
    Do not use $\backslash${\tt{section}} anymore after $\backslash${\tt{appendix}}, only $\backslash${\tt{section*}}.
    If you have multiple appendixes use $\backslash${\tt{appendices}} then use $\backslash${\tt{section}} to start each appendix.
    You must declare a $\backslash${\tt{section}} before using any $\backslash${\tt{subsection}} or using $\backslash${\tt{label}} ($\backslash${\tt{appendices}} by itself
    starts a section numbered zero.)}

%{\appendices
%\section*{Proof of the First Zonklar Equation}
%Appendix one text goes here.
% You can choose not to have a title for an appendix if you want by leaving the argument blank
%\section*{Proof of the Second Zonklar Equation}
%Appendix two text goes here.}

\section{References Section}
You can use a bibliography generated by BibTeX as a .bbl file. BibTeX
documentation can be easily obtained at:
http://mirror.ctan.org/biblio/bibtex/contrib/doc/ The IEEEtran BibTeX style
support page is: http://www.michaelshell.org/tex/ieeetran/bibtex/

% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
\section{Simple References}
You can manually copy in the resultant .bbl file and set second argument of
$\backslash${\tt{begin}} to the number of references (used to reserve space for
the reference number labels box).

>>>>

\section{Discussion}

\subsubsection{Humans Identify Phishing Differently}

Modern email systems involve multiple layers of protection against phishing
attacks. Many email senders include checks for phishing as emails get sent.
Most email systems include at least one, and often more than one technical
system that filters out emails that are believed to be spam or phishing. Many
of these systems also label emails as possibly phishing, as a warning to users
(e.g., Google’s email system [25]). And end users read emails and make
legitimacy determinations on their own.

Reason’s Swiss Cheese Model of filtering [28] suggests that when there is a
chain of filters like this, the filters work best when each filter works on
different principles or using different information than other filters in the
chain. If two filters use the same information (e.g. sender from email ad-
dress) in similar ways, then the holes in the cheese line up and malicious
emails that get through one filter are also likely to get through the other.
However, if two filters use different information, or operate on the
information in fundamentally different ways, then each filter is likely to
catch messages that the other filter misses, and including both filters makes
the system more resilient to attacks than only including one.

In this paper, we present evidence that this final filter – humans reading
emails and determining if an email is le- gitimate – operates in a very
different way, using different knowledge and capabilities, than almost all of
the technical filters. We found that humans possess important information that
technical phishing filters do not have. They rely on their familiarity with
related emails received in the past (72\%) and their expectations of incoming
emails (95\%) to make sense of and become suspicious of phishing emails. This
knowledge is highly contextual and very unique to each individual and their
experiences. In addition, humans use their knowledge of what was typical in
emails they received in the past to spot unexpected and missing important
pieces of information in new emails. This information is critical for detecting
zero-day phishing attacks, which technical solutions rarely detect [12].

Our respondents were able to notice the nature of the email (e.g. 78\% noticed
it was personal) and the email account in which the email was received. This
requires knowledge of all email accounts a person has and the kinds of
communications expected in each account based on how and what the person
chooses to use each account for. It is very complex and chal- lenging for
technical filters to acquire such knowledge and apply it accordingly, lest they
surveil individuals.

Second, we found that humans possess unique capabilities that they use to
identify phishing messages, which technical filters do not have. 94\% of the
non-expert respondents were able of identify what action the email was asking
them to do, and over three quarters said they explicitly noticed this about the
email. Requests for action are not commonly part of many spam and phishing
filters, and when they are, they are often limited in scope mostly by language
issues (e.g. checking if the email contains a link to a login page and
verifying if the login page is legitimate [23]). Even non-experts are highly
attuned to these requests and can confidently identify them.

When filtering, humans also have an investigative ability that technical
filters lack: they can choose to take additional time and look up more
information from third party sources. A number of our respondents indicated
that they would ask colleagues for advice or try to contact the purported
sender of the email.

The above are capabilities and knowledge that humans have, but technical
phishing filters lack. Following the logic of the Swiss Cheese Model, relying
on both humans and technical filtering in combination is better than just
relying on one or the other. In recent years, organizations have been relying
more heavily on automated phishing detection. Our findings suggest that
reducing the diversity of filters may leave systems vulnerable to phishing, and
that approaching end user training differently could strengthen strategies for
preventing harm from phishing.

Much of the advice about phishing in the IT commu- nity involves preventing
messages from ever getting to end users [14], rather than trying to educate end
users. Because end users are able to filter messages in fundamentally dif-
ferent ways than technical filters, it would be more valuable to spend some
money and resources improving the ability of end users to have a significant
role in detecting phishing messages. Too much phishing training focuses on
technical details (like url parsing [19, 30]) or behavioral changes (like not
clicking [20, 35]), instead of trying to strengthen the ca- pabilities that are
unique to humans. In this paper, we have presented evidence of some of the
knowledge and capabilities that humans have which can be leveraged to enhance
phishing training and detection, e.g. forming expectations for emails and
asking other people for information.

As the Swiss Cheese Model points out, in a series of filters, putting all of
your resources into one layer of filters in exclu- sion to others removes the
benefits you get from a defense in depth strategy. It is often better to have
two imperfect filters that operate on different principles or information than
it is to have one filter that is highly optimized but limited.

\subsubsection{Similar to Expert Phishing Detection?}

Our findings also have implications for identifying similarities between expert
and non-expert user phishing email detection. Wash [34] conducted a detailed
study of how people detect phishing emails. That study was conducted with IT
experts – people with IT training and professional experience that allows them
to successfully detect phishing emails. We ex- tended that model, and based
many of our questions on that extended model, partially to try to determine if
features of that model are also present in how non-experts detect phishing.

In this paper, we are able to validate parts of his model with a non-expert
population. Wash also pointed out that in addition to IT expertise, being a
knowledge worker can provide expertise in managing email that is relevant to
phishing detection. Our sample is not IT experts, and it is also not primarily
knowledge workers who deal with email constantly.

In particular, we are able to validate that non-experts do have expectations
about what should be present in emails and notice when those things are
different. We are also able to validate that even in non-experts, people’s
attention is focused on what the email is requesting that they do; almost
everyone in our study was able to identify what request the email was making.
We validated that our non-experts self-reported that they frequently had gut
feelings that something was off about the emails, helping them become
suspicious. We were able to validate that people would frequently take explicit
steps to investigate an email that they found to be suspicious. And we were
able to validate that non-experts were able to con- clusively decide whether an
email was a phishing email or not. This lends support to the implication that
expertise about one’s own email inbox is an important and yet underutilized
aspect of phishing detection training.

We were not able to validate all aspects of Wash’s model with non-experts. In
particular, Wash’s model includes a chronological ordering of stages – first
sensemaking, then suspicion, then acting. Our study is a survey and was unable
to determine a chronological ordering that things happened in, and as such, we
are not sure that things necessarily happen for non-experts in the order that
Wash proposes.

\subsubsection{Implications for Phishing Prevention}

Email users engage in complex investigations of suspicious emails before they
determine if the email is phishing, but current training and technologies do
not support these investigations. Our findings suggest that phishing training
could support user investigations better by encouraging users to delay taking
actions until finalizing their investigation and encouraging email users to
leverage peer capabilities (such as asking a friend for help). Additionally,
companies that send email can provide helpdesk-style support to help users
determine if the company actually sent the email to the user. Email clients
could better support investigations by including a “help me troubleshoot this
email” button, with contextual- ized suggestions for investigation.

\section{Limitations}

This paper is about people, their cognition, and how they successfully detect
phishing. It is not about phishing emails. A survey is not a good method for
collecting underlying ground truth data on the actual phishing emails or
detection failures, because of selection bias and imperfect memory.

Recalling a phishing email prompted recollection of a specific instance,
allowing the survey to investigate the processes that people use to detect
phishing emails in their inbox. The answers we received were only about this
one specific incident, and do not necessarily represent other incidents that
the person was involved in; however, across respondents, these answers do
represent a variety of the types of phishing incidents that non-experts
encounter. Past research has focused almost exclusively on detection failures
and fixing those failures; we instead look at what is working well in phishing
detection and what should be supported.

Since this is a survey, we can only ask detailed questions about things we know
about ahead-of-time. We based our survey questions on Wash’s investigation of
expert phishing detection [34]. We are not able to determine if the non-experts
also use additional methods that were not present in Wash’s experts. That is,
we seek to learn which of these experts’ methods are also used by non-experts,
but we cannot learn anything about non-expert methods that are unique to non-
experts. Therefore, we do not claim that these methods are a comprehensive
description of how non-experts identify phish- ing; instead, we characterize
some methods that they do use.

\section{Conclusion}
Phishing is a cybersecurity threat that many people experience; almost half of
the people eligible for our survey could identify at least one specific
phishing email that they received. These people have stories about phishing
experiences that they can share with others, and we suspect these stories form
an important part of how email users learn about phishing.

We found that many of the techniques that experts use to identify phishing
  [34], such as noticing minor discrepancies, forming expectations about what the
email should look like and noticing differences from those expectations, and
becoming suspicious and investigating the email more closely, are also present
in how non-experts detect phishing emails.

We also found that much of the information that non-experts use when
identifying phishing cannot be replicated by technical phishing detection
systems. End users know the purpose (business, personal) of email accounts they
receive emails at, and pay attention to that fact. They know whether an email
is expected, and are able to compare it against other, similar emails they have
received in the past (phishing emails often feel familiar). Additionally, these
non-experts have investigative abilities, such as delaying responding to emails
and asking the sender for confirmation or more information, that technical
phishing filters don’t possess. Targeting future phishing training at improving
the use of this unique knowledge and expanding the use of these abilities is
likely to yield improvement in phishing protection.

@@

%   {\appendix[Proof of the Zonklar Equations]
%     Use $\backslash${\tt{appendix}} if you have a single appendix:
%     Do not use $\backslash${\tt{section}} anymore after $\backslash${\tt{appendix}}, only $\backslash${\tt{section*}}.
%     If you have multiple appendixes use $\backslash${\tt{appendices}} then use $\backslash${\tt{section}} to start each appendix.
%     You must declare a $\backslash${\tt{section}} before using any $\backslash${\tt{subsection}} or using $\backslash${\tt{label}} ($\backslash${\tt{appendices}} by itself
%     starts a section numbered zero.)}

% %{\appendices
% %\section*{Proof of the First Zonklar Equation}
% %Appendix one text goes here.
% % You can choose not to have a title for an appendix if you want by leaving the argument blank
% %\section*{Proof of the Second Zonklar Equation}
% %Appendix two text goes here.}

% \section{References Section}
% You can use a bibliography generated by BibTeX as a .bbl file. BibTeX
% documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/ The IEEEtran BibTeX style
% support page is: http://www.michaelshell.org/tex/ieeetran/bibtex/

% % argument is your BibTeX string definitions and bibliography database(s)
% %\bibliography{IEEEabrv,../bib/paper}
% %
% \section{Simple References}
% You can manually copy in the resultant .bbl file and set second argument of
% $\backslash${\tt{begin}} to the number of references (used to reserve space for
% the reference number labels box).
